Specification and Verification of Stencil Computation Shape

### 2016-11-15 paper.tex
evaluation stubs

\title{Verification of Stencil Computations with Spatial
  Specifications}
%\titlebanner{DRAFT -- Do not distribute}
\authorinfo{}{}{}
%\preprintfooter{DO NOT DISTRIBUTE}

@@

>>>>

\title{Specification and Verification of Stencil Computation Shape}
%\titlebanner{DRAFT -- Do not distribute}
\authorinfo{}{}{}
%\preprintfooter{DO NOT DISTRIBUTE}

@@

\subsection{Core hypotheses}

\paragraph{Hypothesis 1: Stencil computations
(as in Definition~\ref{def:stencil}) are a common programming pattern
in numerical code}

% Number of stencils (tickAssign) / number of loops
% Percentage of a code base that is taken up by stencils

\paragraph{Hypothesis 2: Most stencil computations
have a regular pattern which can be captured with a simple
language of contiguous regions}

% Number of stencils we give a spec to (where a spec declaration to n
% variables is counted n times) as percentage of number of stencils

%
\subsection{Analysing the design of our specifications}

% 1. How may are just reflexive and how many some reflexive

% 2. Break down of "interesting specifications" (contain more than
% just reflexive)
%   - Single-action, histogram on depths
%   - Single-action + irreflexives, histogram on depths
%   - Bounded
%   - Multi-action combined only by *
%   - Multi-action combined also by +, histogram of tree depths

% Present not just percentages but concrete numbers
